\SW: I. Crowd-sourcing the Discovery of Gravitational Lenses

### 2015-04-21 doc/sw-system.tex
Finished going through Anu's comments, closes #112

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/CFHTLS_2013-10-29_10:16:35_probabilities.png}
\caption{Typical \SW agent confusion matrix elements. At a particular
snapshot, 200 randomly-selected agents are shown distributed over the unit plane, with a
tendency to move towards the ``astute'' region in the upper right hand
quadrant as each agent's volunteer views more images. Yellow point size is
proprtional to the number of images classified; green point size shows
agent-perceived ``skill.''}
\label{fig:swap:agent-probabilities}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

During \StageOne classification of the \cfhtls images, we assigned a prior
probability for each image to contain a lens of $2\times10^{-4}$, based on a
rough estimate of the number of expected lenses in the survey, and the fraction
of the survey area covered by each image. We then assigned two values of the
images' posterior probability, $\pr(\LENS|C,T)$, to define ``detection'' and
``rejection'' thresholds. These were set to be 0.95 and (approximately
symmetrically in the logarithm of probability), $10^{-7}$. Subjects that
attained probability of less than the rejection threshold were scheduled for
retirement and subsequently ignored by the analysis code. Subjects crossing the
detection threshold were also subsequently ignored, but they were not
retired from the website, just so that more volunteers could see them.
The progress of the subjects is illustrated in
\Fref{fig:swap:subject-trajectories}. Subjects appear on this plot at the tip of
the arrow, at zero classifications and prior probability; they then drift
downwards as they are classified by the crowd, with each agent applying the
appropriate kick in probability based on what it hears its volunteer say.
Encouragingly, sims (blue) tend to end up with high probability, while duds
(red) pile up at low probability; test subjects (black) mostly drift to low
probability, but some go the other way. The latter will help make up the
candidate sample. As this plot shows, around 10 classifications are typically
required for a subject to reach the retirement (or detection) threshold.

The analysis code was run every night during the project, and subjects retired
in batches after its completion. This introduced some inefficiency, because
some classifications were accumulated in the time between them crossing the
rejection threshold and the subject actually being retired from the website.
As subjects were retired from the site, more subjects were activated. In this
way, the volunteers who down-voted images for not containing any lensed
features enabled new images to be shown to other members of the community.

When all the subjects had either been retired, or classified around 10 times or
more, the web app was paused and reconfigured for \StageTwo. The sample of
subjects classified during \StageTwo was selected to be all those that passed
the detection threshold ($\pr(\LENS|C,T) > 0.95$) at \StageOne. These were
classified for one week, with no retirement but a maximum classification number
of 50 each. The number of subjects at \StageTwo was small enough that we did not
need to retire any: instead, we simply collected classifications for a fixed
period of time (about 4 weeks). Without the time pressure motivating the online
calculation of \StageOne, we carried out an offline analysis
(\Sref{sec:swap:offline} above) of the  \StageTwo classifications, for
comparison and as we will see in the next section, improving the pipeline
performance.

@@

We investigated the source of the incompleteness and impurity visible in
\Fref{fig:results:sample:CP}, by examining the \StageTwo false negatives and
false positives, and their behaviour as they are classified using the online
analysis trajectory plots introduced in \Sref{sec:swap}
(\Fref{fig:swap:subject-trajectories}).
\Fref{fig:discuss:performance:trajectories} shows 2 example simulated lenses
that were missed ($\pr(\LENS|C,T) < 10^{-5}$) by the \SW system (top row),
and 2 example
non-lenses that were incorrectly flagged as candidates ($\pr(\LENS|C,T) >
0.95$) by the \SW system (bottom row).
While the final \StageTwo analysis was done offline,
these trajectory plots still serve to illustrate the approximate
classification histories of the subjects.

In some cases the rejection of the false negatives is understandable: the
lensed features are faint, or in some cases, appear somewhat unrealistic compared to real lenses.
However, in other cases a reasonably obvious lens was passed over.  This
mainly seems to be due to noise in the system: when only low-skill classifiers
view a subject, all the updates to its posterior probability are small, and if
none are very confident about the presence of lensing, the subject follows a
random walk down its trajectory plot. This can be seen in the top left panel
of Figure \Fref{fig:discuss:performance:trajectories}.

@@

Mistakes by both high and low skill classifiers could be reduced by improving
the training in the system, which could be done in several ways. One is to
make more training images available to those who want or need it. A basic
level of training images are needed for SWAP to build up an accurate picture
of each classifier's skill -- but one could imagine volunteers {\it choosing}
to see more training images (still at random) in their stream. We could also
experiment with providing greater training rates early on for all volunteers;
the risk associated with this is that retention rates may drop if too few
``fresh'' test images are shown early on. Another way of improving the
training could be to provide more information about what lenses do. In this
project, the Spotter's Guide, and the Science, FAQ and About pages were always available on the site, but as a
passive background resource. We might consider providing more links to this
guide in the feedback messages shown to the classifiers as they go -- or
perhaps extending these messages to themselves include more explanations and
example images. We might also investigate a more dynamic Spotter's Guide: a
set of manipulable model lenses illustrating all the possible image
configurations that that those deflectors can make could help volunteers gain
understanding of what lensed features can look like very quickly. Such a toy
is under development.

@@

However, most identification failures (around 60\%) seem to be due to the
random walk problem. Short, random direction steps arise from low skill
classifiers, arising from classifier inexperience (\Sref{sec:results:crowd}).
While improved training will help reduce this effect, it is here
that targeted task assignment could also help improve system performance, by
bringing higher skill volunteers in to the mix. We
advertised \StageTwo of the current project to all registered users; it was
taken up by \StageOne veterans with a broad range of skill, and also picked up a
significant number of new users who did not have enough time to aquire high
skill (since \StageTwo was quite short): of the 1964 volunteers who took part in
the \StageTwo classification round, only 774 were veterans from \StageOne.

\Fref{fig:discuss:performance:stage1vstage2} shows how the \StageOne skill maps
on to \StageTwo skill and contribution.
This figure suggests that there may be some benefit to opening \StageTwo on the
basis of \StageOne agent skill, in order to reduce the noise in the system
generated by new and low skill volunteers in this more difficult
classification stage.  A simple implementation of this would be to switch the
web app to the \StageTwo version when either a certain \StageOne skill (and/or
effort) threshold was passed. Good strategy would probably be to switch back
to \StageOne after some number of \StageTwo classifications (to avoid losing the
high skill users from \StageOne entirely), and also to make it very clear which
stage the classifier was at (since \StageTwo requires more careful attention).
This is something we plan to experiment with in future.

Finally, there could be some performance gains to be made by improving the
SWAP agent model, or its implementation. Low skill is typically a result  of
inexperience (\Sref{sec:results:crowd}), but it could be the agent that is
inexperienced as well as the classifier or its agent. In a future paper we
plan to investigate the use of the test images as well as the training images
in accelerating the agent's learning (Davis et al, in preparation). We also
plan to investigate the use of offline analysis at \StageOne, for the same
reason (see also \Sref{sec:discuss:efficiency} below.)
One might also consider looking at
introducing more conditional dependences in the confusion matrix elements, to
allow for some classifiers having greater skill in spotting one type of lens
than another, or, more generally, as a function of lens property (such as
colour, brightness, and image separation). In the current model, all agents are
considered to be completely independent, whereas in fact we might expect there
to be significant clustering of the confusion matrix elements. A hierarchical
model for the crowd, with hyper-parameters describing the distribution of
confusion matrix elements across the population, may well accelerate the agent
learning process by including the notion of one agent being likely to be
similar to its neighbours. Finally, it is worth noting that the model of
\citet{IBCC} explicitly avoids the assumption of the agent confusion matrix
elements being constant in time, allowing the development of volunteer skill
to be more accurately tracked -- and that they did see some time-evolution in
the supernova zoo classifiers' skill. Finding a way to incorporate such a
learning model into SWAP, while retaining its statistically online character
is an interesting challenge for future work.

@@

It is clear that to increase the efficiency of the system we need to reduce
the time lag between the classification being made and its outcome being
analyzed. The optimal way to do this would be to have the web app itself
analyze the classifications in a fully online system. This is under
investigation for future projects. With the classification data being analyzed
in real time, there may still be a place for a daily or weekly offline
analysis: this could potentially reduce the false negative and false positive
rates by ``resurrecting'' subjects that had been retired by the online system
before the agents had time to learn enough about their classifier's high
skill.

If the system efficiency could be improved by a factor of three, we would expect
the characteristic completion time $\tau_0$  in \Eref{eq:speed} to decrease by
roughly the same factor, suggesting that a dataset of $10^4$~images could be
searched for lenses by a crowd of $10^4$ volunteers in about 6 days.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/CFHTLS_2013-10-29_10:16:35_probabilities.png}
\caption{Typical \SW agent confusion matrix elements. At a particular
snapshot, 200 randomly-selected agents are shown distributed over the unit plane, with a
tendency to move towards the ``astute'' region in the upper right hand
quadrant as each agent's volunteer views more images. Yellow point size is
proprtional to the number of images classified; green point size shows
agent-perceived ``skill'' (\Aref{appendix:swap}).}
\label{fig:swap:agent-probabilities}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

During the \StageOne classification of the \cfhtls images, we assigned a prior
probability for each image to contain a lens of $2\times10^{-4}$, based on a
rough estimate of the number of expected lenses in the survey, and the fraction
of the survey area covered by each image. We then assigned two values of the
images' posterior probability, $\pr(\LENS|C,T)$, to define ``detection'' and
``rejection'' thresholds. These were set to be 0.95 and (approximately
symmetrically in the logarithm of probability), $10^{-7}$. Subjects that
attained probability of less than the rejection threshold were scheduled for
retirement and subsequently ignored by the analysis code. Subjects crossing the
detection threshold were also subsequently ignored, but they were not
retired from the website, just so that more volunteers could see them.

The progress of the subjects during the online analysis is illustrated in
\Fref{fig:swap:subject-trajectories}. Subjects appear on this plot at the tip of
the arrow, at zero classifications and prior probability; they then drift
downwards as they are classified by the crowd, with each agent applying the
appropriate kick in probability based on what it hears its volunteer say.
Encouragingly, sims (blue) tend to end up with high probability, while duds
(red) pile up at low probability; test subjects (black) mostly drift to low
probability, but some go the other way. The latter will help make up the
candidate sample. As this plot shows, around 10 classifications are typically
required for a subject to reach the retirement (or detection) threshold.

The online analysis code was run every night during the project, and subjects retired
in batches after its completion. This introduced some inefficiency, because
some classifications were accumulated in the time between them crossing the
rejection threshold and the subject actually being retired from the website.
(We quantify this inefficiency in \Sref{sec:discuss:efficiency} below.)
As subjects were retired from the site, more subjects were activated. In this
way, the volunteers who down-voted images for not containing any lensed
features enabled new images to be shown to other members of the community.

When all the subjects had either been retired, or classified around 10 times or
more, the web app was paused and reconfigured for \StageTwo. The sample of
subjects classified during \StageTwo was selected to be all those that passed
the detection threshold ($\pr(\LENS|C,T) > 0.95$) at \StageOne. These were
classified for one week, with no retirement but a maximum classification number
of 50 each. The number of subjects at \StageTwo was small enough that we did not
need to retire any: instead, we simply collected classifications for a fixed
period of time (about 4 weeks). Without the time pressure motivating an
online-only calculation (as there had been during \StageOne), we carried out an
offline analysis (\Sref{sec:swap:offline} above) of the  \StageTwo
classifications as well, both  for comparison and as we will see in the next
section, to improve the pipeline performance.

@@

We investigated the source of the incompleteness and impurity visible in
\Fref{fig:results:sample:CP}, by examining the \StageTwo false negatives and
false positives, and their behaviour as they are classified using the online
analysis trajectory plots introduced in \Sref{sec:swap}
(\Fref{fig:swap:subject-trajectories}).
\Fref{fig:discuss:performance:trajectories} shows 2 example simulated lenses
that were missed ($\pr(\LENS|C,T) < 10^{-5}$) by the \SW system (top row),
and 2 example
non-lenses that were incorrectly flagged as candidates ($\pr(\LENS|C,T) >
0.95$) by the \SW system (bottom row).

In some cases the rejection of the false negatives is understandable: the
lensed features are faint, or in some cases, appear somewhat unrealistic compared to real lenses.
However, in other cases a reasonably obvious lens was passed over.  This
mainly seems to be due to noise in the system: when only low-skill classifiers
view a subject, all the updates to its posterior probability are small, and if
none are very confident about the presence of lensing, the subject follows a
random walk down its trajectory plot. This can be seen in the top left panel
of \Fref{fig:discuss:performance:trajectories}.

@@

Mistakes by both high and low skill classifiers could be reduced by improving
the training in the system, which could be done in several ways. One is to make
more training images available to those who want or need it. A basic level of
training images are needed for SWAP to build up an accurate picture of each
classifier's skill -- but one could imagine volunteers {\it choosing} to see
more training images (still at random) in their stream. We could also experiment
with providing greater training rates early on for all volunteers; the risk
associated with this is that retention rates may drop if too few ``fresh'' test
images are shown early on. Another way of improving the training could be to
provide more information about what gravitational lens systems look like. In
this project, the Spotter's Guide, and the Science, FAQ and About pages were
always available on the site, but as a passive background resource. We might
consider providing more links to this guide in the feedback messages shown to
the classifiers as they go -- or perhaps extending these messages to themselves
include more explanations and example images. We might also investigate a more
dynamic Spotter's Guide: a set of manipulable model lenses illustrating all the
possible image configurations that those deflectors can make could help
volunteers very quickly gain understanding of what lensed features can look
like. Such a tool is under development.\footnote{\texttt{http://slowe.github.io/LensToy}}

@@

However, identification failures (around 60\%, from inspection of a random sample)
seem to be due to the statistical noise associated with
the many short, semi-random direction steps arising from classifications made by
low skill, inexperienced
classifiers (\Sref{sec:results:crowd}).
While improved training will help reduce this effect, it is here
that targeted task assignment could also help improve system performance, by
bringing higher skill volunteers in when needed. We
advertised \StageTwo of the current project to all registered users; it was
taken up by \StageOne veterans with a broad range of skill, and also picked up a
significant number of new users who did not have enough time to aquire high
skill (since \StageTwo was quite short): of the 1964 volunteers who took part in
the \StageTwo classification round, only 774 were veterans from \StageOne.

\Fref{fig:discuss:performance:stage1vstage2} shows how the \StageOne skill maps
on to \StageTwo skill and contribution. This figure suggests that, while the
gains are likely small (since  most of the contribution is still made by high
skill volunteers),  there could have been some benefit to opening \StageTwo on
the basis of \StageOne agent skill, in order to reduce the noise in the system
generated by new and low skill volunteers in this more difficult classification
stage.  In future, dynamically allocating subjects to volunteers according to
their agents' skill could alleviate this issue.
%A simple implementation of this would be to switch the web app to the \StageTwo
%version when either a certain \StageOne skill (and/or effort) threshold was
%passed. Good strategy would probably be to switch back to \StageOne after some
%number of \StageTwo classifications (to avoid losing the high skill users from
%\StageOne entirely), and also to make it very clear which stage the classifier
%was at (since \StageTwo requires more careful attention).
This is something we plan to experiment with in future.

Finally, there could be some performance gains to be made by improving the
SWAP agent model, or its implementation. Low skill is typically a result  of
inexperience (\Sref{sec:results:crowd}), but it could be the agent that is
inexperienced as well as the classifier or its agent. In a future paper we
plan to investigate the use of the test images as well as the training images
in accelerating the agent's learning (Davis et al, in preparation). We also
plan to investigate the use of offline analysis at \StageOne, for the same
reason (see also \Sref{sec:discuss:efficiency} below.)
One might also consider looking at
introducing more conditional dependences in the confusion matrix elements, to
allow for some classifiers having greater skill in spotting one type of lens
than another, or, more generally, as a function of lens property (such as
colour, brightness, and image separation). In the current model, all agents are
considered to be completely independent, whereas in fact we might expect there
to be significant clustering of the confusion matrix elements in the $\PD - \PL$
plane. A hierarchical
model for the crowd, with hyper-parameters describing the distribution of
confusion matrix elements across the population, may well accelerate the agent
learning process by including the notion of one agent being likely to be
similar to its neighbours. Finally, it is worth noting that the model of
\citet{IBCC} explicitly avoids the assumption of the agent confusion matrix
elements being constant in time (as was assumed in \Sref{sec:swap}),
allowing the development of volunteer skill
to be more accurately tracked -- and that they did see some time-evolution in
the supernova zoo classifiers' skill. Finding a way to incorporate such a
learning model into SWAP while retaining its online character
is an interesting challenge for future work.

@@

It is clear that to increase the efficiency of the system we need to reduce the
time lag between the classification being made and its outcome being analyzed.
The optimal way to do this would be to have the web app itself analyze the
classifications in real time. This is under investigation for future projects.
There may still be a place for a daily or weekly offline analysis: this could
potentially reduce the false negative and false positive rates by
``resurrecting'' subjects that had been retired by the online system before the
agents had time to learn enough about their classifier's high skill.

If, as expected, the system efficiency could indeed be improved by a factor of
three via real-time classification analysis, we would expect the characteristic
completion time $\tau_0$  in \Eref{eq:speed} to decrease by roughly the same
factor, suggesting that a dataset of $10^4$~images could be searched for lenses
by a crowd of $10^4$ volunteers in about 6 days.
